\Title

### 2020-12-23 manuscript/manuscript.tex

% Import files with parameter values generated by notebooks
\newcommand{\Gal}{Gal}
\input{synthetic-surveys.tex}
\input{parameters-ground-survey.tex}
\input{parameters-airborne-survey.tex}
\input{best-parameters-ground-survey.tex}
\input{best-parameters-airborne-survey.tex}
\input{source-layouts-schematics.tex}

@@

@@

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic ground survey. The table also contains the set of parameters
        that generates the best prediction for each source distribution and its
        corresponding RMS score (in mGal).
    }
    \label{tab:parameters-ground-survey}
    \begin{tabular}{c c l c c c}
        \textbf{Source layout}
            & \textbf{Depth type}
            & \multicolumn{1}{c}{\textbf{Parameters}}
            & \textbf{Values}
            & \textbf{Best}
            & \textbf{RMS (mGal)} \\
        \toprule

        \multirow{8}{*}{Source Below Data}
            & \multirow{2}{*}{Constant Depth}
                & Depth (m)
                & \GroundSourceBelowDataConstantDepthDepth
                & \BestGroundSourceBelowDataConstantDepthDepth
                & \multirow{2}{*}{
                    \BestGroundSourceBelowDataConstantDepthRms
                  } \\
            &
                & Damping
                & \GroundSourceBelowDataConstantDepthDamping
                & \BestGroundSourceBelowDataConstantDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{2}{*}{Relative Depth}
                & Depth (m)
                & \GroundSourceBelowDataRelativeDepthDepth
                & \BestGroundSourceBelowDataRelativeDepthDepth
                & \multirow{2}{*}{
                    \BestGroundSourceBelowDataRelativeDepthRms
                  } \\
            &
                & Damping
                & \GroundSourceBelowDataRelativeDepthDamping
                & \BestGroundSourceBelowDataRelativeDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{4}{*}{Variable Depth}
                & Depth (m)
                & \GroundSourceBelowDataVariableDepthDepth
                & \BestGroundSourceBelowDataVariableDepthDepth
                & \multirow{4}{*}{
                    \BestGroundSourceBelowDataVariableDepthRms
                  } \\
            &
                & Depth factor
                & \GroundSourceBelowDataVariableDepthDepthFactor
                & \BestGroundSourceBelowDataVariableDepthDepthFactor
                & \\
            &
                & K nearest
                & \GroundSourceBelowDataVariableDepthKNearest
                & \BestGroundSourceBelowDataVariableDepthKNearest
                & \\
            &
                & Damping
                & \GroundSourceBelowDataVariableDepthDamping
                & \BestGroundSourceBelowDataVariableDepthDamping
                & \\
        \midrule

        \multirow{11}{*}{Block Averaged Sources}
            & \multirow{3}{*}{Constant Depth}
                & Depth (m)
                & \GroundBlockAveragedSourcesConstantDepthDepth
                & \BestGroundBlockAveragedSourcesConstantDepthDepth
                & \multirow{3}{*}{
                    \BestGroundBlockAveragedSourcesConstantDepthRms
                  } \\
            &
                & Spacing (m)
                & \GroundBlockAveragedSourcesConstantDepthSpacing
                & \BestGroundBlockAveragedSourcesConstantDepthSpacing
                & \\
            &
                & Damping
                & \GroundBlockAveragedSourcesConstantDepthDamping
                & \BestGroundBlockAveragedSourcesConstantDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{3}{*}{Relative Depth}
                & Depth (m)
                & \GroundBlockAveragedSourcesRelativeDepthDepth
                & \BestGroundBlockAveragedSourcesRelativeDepthDepth
                & \multirow{3}{*}{
                    \BestGroundBlockAveragedSourcesRelativeDepthRms
                  } \\
            &
                & Spacing (m)
                & \GroundBlockAveragedSourcesRelativeDepthSpacing
                & \BestGroundBlockAveragedSourcesRelativeDepthSpacing
                & \\
            &
                & Damping
                & \GroundBlockAveragedSourcesRelativeDepthDamping
                & \BestGroundBlockAveragedSourcesRelativeDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{5}{*}{Variable Depth}
                & Depth (m)
                & \GroundBlockAveragedSourcesVariableDepthDepth
                & \BestGroundBlockAveragedSourcesVariableDepthDepth
                & \multirow{5}{*}{
                    \BestGroundBlockAveragedSourcesVariableDepthRms
                  } \\
            &
                & Depth factor
                & \GroundBlockAveragedSourcesVariableDepthDepthFactor
                & \BestGroundBlockAveragedSourcesVariableDepthDepthFactor
                & \\
            &
                & K nearest
                & \GroundBlockAveragedSourcesVariableDepthKNearest
                & \BestGroundBlockAveragedSourcesVariableDepthKNearest
                & \\
            &
                & Spacing (m)
                & \GroundBlockAveragedSourcesVariableDepthSpacing
                & \BestGroundBlockAveragedSourcesVariableDepthSpacing
                & \\
            &
                & Damping
                & \GroundBlockAveragedSourcesVariableDepthDamping
                & \BestGroundBlockAveragedSourcesVariableDepthDamping
                & \\
        \midrule

        \multirow{4}{*}{Grid Sources}
            & \multirow{4}{*}{Constant Depth}
                & Depth (m)
                & \GroundGridSourcesConstantDepthDepth
                & \BestGroundGridSourcesConstantDepthDepth
                & \multirow{4}{*}{
                    \BestGroundGridSourcesConstantDepthRms
                  } \\
            &
                & Spacing (m)
                & \GroundGridSourcesConstantDepthSpacing
                & \BestGroundGridSourcesConstantDepthSpacing
                & \\
            &
                & Damping
                & \GroundGridSourcesConstantDepthDamping
                & \BestGroundGridSourcesConstantDepthDamping
                & \\
    \end{tabular}
\end{table*}

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic airborne survey. The table also contains the set of
        parameters that generates the best prediction for each source
        distribution and its corresponding RMS score (in mGal).
    }
    \label{tab:parameters-airborne-survey}
    \begin{tabular}{c c l c c c}
        \textbf{Source layout}
            & \textbf{Depth type}
            & \multicolumn{1}{c}{\textbf{Parameters}}
            & \textbf{Values}
            & \textbf{Best}
            & \textbf{RMS (mGal)} \\
        \toprule

        \multirow{8}{*}{Source Below Data}
            & \multirow{2}{*}{Constant Depth}
                & Depth (m)
                & \AirborneSourceBelowDataConstantDepthDepth
                & \BestAirborneSourceBelowDataConstantDepthDepth
                & \multirow{2}{*}{
                    \BestAirborneSourceBelowDataConstantDepthRms
                  } \\
            &
                & Damping
                & \AirborneSourceBelowDataConstantDepthDamping
                & \BestAirborneSourceBelowDataConstantDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{2}{*}{Relative Depth}
                & Depth (m)
                & \AirborneSourceBelowDataRelativeDepthDepth
                & \BestAirborneSourceBelowDataRelativeDepthDepth
                & \multirow{2}{*}{
                    \BestAirborneSourceBelowDataRelativeDepthRms
                  } \\
            &
                & Damping
                & \AirborneSourceBelowDataRelativeDepthDamping
                & \BestAirborneSourceBelowDataRelativeDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{4}{*}{Variable Depth}
                & Depth (m)
                & \AirborneSourceBelowDataVariableDepthDepth
                & \BestAirborneSourceBelowDataVariableDepthDepth
                & \multirow{4}{*}{
                    \BestAirborneSourceBelowDataVariableDepthRms
                  } \\
            &
                & Depth factor
                & \AirborneSourceBelowDataVariableDepthDepthFactor
                & \BestAirborneSourceBelowDataVariableDepthDepthFactor
                & \\
            &
                & K nearest
                & \AirborneSourceBelowDataVariableDepthKNearest
                & \BestAirborneSourceBelowDataVariableDepthKNearest
                & \\
            &
                & Damping
                & \AirborneSourceBelowDataVariableDepthDamping
                & \BestAirborneSourceBelowDataVariableDepthDamping
                & \\
        \midrule

        \multirow{11}{*}{Block Averaged Sources}
            & \multirow{3}{*}{Constant Depth}
                & Depth (m)
                & \AirborneBlockAveragedSourcesConstantDepthDepth
                & \BestAirborneBlockAveragedSourcesConstantDepthDepth
                & \multirow{3}{*}{
                    \BestAirborneBlockAveragedSourcesConstantDepthRms
                  } \\
            &
                & Spacing (m)
                & \AirborneBlockAveragedSourcesConstantDepthSpacing
                & \BestAirborneBlockAveragedSourcesConstantDepthSpacing
                & \\
            &
                & Damping
                & \AirborneBlockAveragedSourcesConstantDepthDamping
                & \BestAirborneBlockAveragedSourcesConstantDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{3}{*}{Relative Depth}
                & Depth (m)
                & \AirborneBlockAveragedSourcesRelativeDepthDepth
                & \BestAirborneBlockAveragedSourcesRelativeDepthDepth
                & \multirow{3}{*}{
                    \BestAirborneBlockAveragedSourcesRelativeDepthRms
                  } \\
            &
                & Spacing (m)
                & \AirborneBlockAveragedSourcesRelativeDepthSpacing
                & \BestAirborneBlockAveragedSourcesRelativeDepthSpacing
                & \\
            &
                & Damping
                & \AirborneBlockAveragedSourcesRelativeDepthDamping
                & \BestAirborneBlockAveragedSourcesRelativeDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{5}{*}{Variable Depth}
                & Depth (m)
                & \AirborneBlockAveragedSourcesVariableDepthDepth
                & \BestAirborneBlockAveragedSourcesVariableDepthDepth
                & \multirow{5}{*}{
                    \BestAirborneBlockAveragedSourcesVariableDepthRms
                  } \\
            &
                & Depth factor
                & \AirborneBlockAveragedSourcesVariableDepthDepthFactor
                & \BestAirborneBlockAveragedSourcesVariableDepthDepthFactor
                & \\
            &
                & K nearest
                & \AirborneBlockAveragedSourcesVariableDepthKNearest
                & \BestAirborneBlockAveragedSourcesVariableDepthKNearest
                & \\
            &
                & Spacing (m)
                & \AirborneBlockAveragedSourcesVariableDepthSpacing
                & \BestAirborneBlockAveragedSourcesVariableDepthSpacing
                & \\
            &
                & Damping
                & \AirborneBlockAveragedSourcesVariableDepthDamping
                & \BestAirborneBlockAveragedSourcesVariableDepthDamping
                & \\
        \midrule

        \multirow{4}{*}{Grid Sources}
            & \multirow{4}{*}{Constant Depth}
                & Depth (m)
                & \AirborneGridSourcesConstantDepthDepth
                & \BestAirborneGridSourcesConstantDepthDepth
                & \multirow{4}{*}{
                    \BestAirborneGridSourcesConstantDepthRms
                  } \\
            &
                & Spacing (m)
                & \AirborneGridSourcesConstantDepthSpacing
                & \BestAirborneGridSourcesConstantDepthSpacing
                & \\
            &
                & Damping
                & \AirborneGridSourcesConstantDepthDamping
                & \BestAirborneGridSourcesConstantDepthDamping
                & \\
    \end{tabular}
\end{table*}

>>>>

% Import files with parameter values generated by notebooks
\newcommand{\Gal}{Gal}
\input{synthetic-surveys.tex}
\input{parameters-ground-survey.tex}
\input{parameters-airborne-survey.tex}
\input{best-parameters-ground-survey.tex}
\input{best-parameters-airborne-survey.tex}
\input{source-layouts-schematics.tex}
\input{boost-overlapping.tex}

@@

\section{Performance of gradient boosted equivalent sources}

Our second goal is to assess the accuracy of the predictions achieved by the
gradient boosting algorithm while registering its performance by comparison
with the non-boosted equivalent sources.

\subsection{Window size}
\label{sec:window-size}

One factor that plays an important role on the performance of the gradient
boosted equivalent sources is the size of the overlapping windows used to create
each set of equivalent sources.
The size of the windows controls the size of the Jacobian matrices
$\tilde{\mathbf{A}_k}$: smaller windows create smaller Jacobian matrices.
Thus, using smaller windows will reduce the amount of computer memory needed to
fit the source coefficients.
Nevertheless, smaller windows may produce less accurate predictions because
their inability to achieve the global minimum of the misfit from
equation~\ref{eq:misfit-unscaled}.
Besides, the window size might also impact on the computation time needed to
fit the source coefficients: smaller windows will generate simpler least-square
problems which are easier to solve, but they will also create more iterations.

We want to assess how the size of the overlapping windows impacts both the
accuracy of the predictions and the computation time needed to fit the source
coefficients in comparison with the performance of the non-boosted equivalent
sources.

We applied the gradient boosted equivalent sources to interpolate the synthetic
airborne survey on the same points of the target grid.
We selected several window sizes to assess how accuracy and performance depend
on that variable.
For each window size we gridded the synthetic data using block-averaged sources
with a spacing of
\SI{\BestAirborneBlockAveragedSourcesRelativeDepthSpacing}{\meter},
a relative depth of
\SI{\BestAirborneBlockAveragedSourcesRelativeDepthDepth}{\meter}, an overlap
of 50\%, and with different values of damping.
Then we compared the resulting interpolations with the target grid in order to
get the best prediction for each window size and the damping value used to
obtain it.

Using the best set of parameters for each window size, we registered the
achieved RMS against the values of the target grid and the time needed to fit
the sources coefficients.
In order to avoid any errors introduced by the way windows are shuffled, the
RMS for each window size was obtained as the mean RMS achieved by using
different random seeds.

\subsection{Overlapping}

Another factor that plays an important role on the performance of the gradient
boosted equivalent sources is the amount of overlap between adjacent windows.
The previous choice of 50\% showed to be sufficiently good to achieve
acceptable accuracy, although a deeper study should be carried out to assess
how the amount of overlap impacts both accuracy and fitting time.

We interpolated the synthetic airborne survey using the gradient boosted
equivalent sources on the same points of the target grid.
The interpolations were carried out using different amount of overlap, from
0\% to 0.95\% with a step size of 0.05\%.
For each overlap we gridded the synthetic data using block-averaged sources
with a spacing of
\SI{\BestAirborneBlockAveragedSourcesRelativeDepthSpacing}{\meter},
a relative depth of
\SI{\BestAirborneBlockAveragedSourcesRelativeDepthDepth}{\meter},
a window size of \BoostOverlappingWindowSize, and with different
values of damping.
Then we compared the resulting interpolations with the target grid in order to
get the best prediction for each overlap and the damping value used to
obtain it.

Using the best set of parameters for each overlap, we registered the achieved
RMS against the values of the target grid and the time needed to fit the
sources coefficients.
The RMS was obtained as the mean RMS achieved by using different random seeds
as we did on~\ref{sec:window-size}.

\section{Gridding Australia gravity data}

@@

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic ground survey. The table also contains the set of parameters
        that generates the best prediction for each source distribution and its
        corresponding RMS score (in mGal).
    }
    \label{tab:parameters-ground-survey}
    \begin{tabular}{c c l c c c}
        \textbf{Source layout}
            & \textbf{Depth type}
            & \multicolumn{1}{c}{\textbf{Parameters}}
            & \textbf{Values}
            & \textbf{Best}
            & \textbf{RMS} \\
        \toprule

        \multirow{8}{*}{Source Below Data}
            & \multirow{2}{*}{Constant}
                & Depth (m)
                & \GroundSourceBelowDataConstantDepthDepth
                & \BestGroundSourceBelowDataConstantDepthDepth
                & \multirow{2}{*}{
                    \BestGroundSourceBelowDataConstantDepthRms
                  } \\
            &
                & Damping
                & \GroundSourceBelowDataConstantDepthDamping
                & \BestGroundSourceBelowDataConstantDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{2}{*}{Relative}
                & Depth (m)
                & \GroundSourceBelowDataRelativeDepthDepth
                & \BestGroundSourceBelowDataRelativeDepthDepth
                & \multirow{2}{*}{
                    \BestGroundSourceBelowDataRelativeDepthRms
                  } \\
            &
                & Damping
                & \GroundSourceBelowDataRelativeDepthDamping
                & \BestGroundSourceBelowDataRelativeDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{4}{*}{Variable}
                & Depth (m)
                & \GroundSourceBelowDataVariableDepthDepth
                & \BestGroundSourceBelowDataVariableDepthDepth
                & \multirow{4}{*}{
                    \BestGroundSourceBelowDataVariableDepthRms
                  } \\
            &
                & Depth factor
                & \GroundSourceBelowDataVariableDepthDepthFactor
                & \BestGroundSourceBelowDataVariableDepthDepthFactor
                & \\
            &
                & K nearest
                & \GroundSourceBelowDataVariableDepthKNearest
                & \BestGroundSourceBelowDataVariableDepthKNearest
                & \\
            &
                & Damping
                & \GroundSourceBelowDataVariableDepthDamping
                & \BestGroundSourceBelowDataVariableDepthDamping
                & \\
        \midrule

        \multirow{11}{*}{Block Averaged Sources}
            & \multirow{3}{*}{Constant}
                & Depth (m)
                & \GroundBlockAveragedSourcesConstantDepthDepth
                & \BestGroundBlockAveragedSourcesConstantDepthDepth
                & \multirow{3}{*}{
                    \BestGroundBlockAveragedSourcesConstantDepthRms
                  } \\
            &
                & Spacing (m)
                & \GroundBlockAveragedSourcesConstantDepthSpacing
                & \BestGroundBlockAveragedSourcesConstantDepthSpacing
                & \\
            &
                & Damping
                & \GroundBlockAveragedSourcesConstantDepthDamping
                & \BestGroundBlockAveragedSourcesConstantDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{3}{*}{Relative}
                & Depth (m)
                & \GroundBlockAveragedSourcesRelativeDepthDepth
                & \BestGroundBlockAveragedSourcesRelativeDepthDepth
                & \multirow{3}{*}{
                    \BestGroundBlockAveragedSourcesRelativeDepthRms
                  } \\
            &
                & Spacing (m)
                & \GroundBlockAveragedSourcesRelativeDepthSpacing
                & \BestGroundBlockAveragedSourcesRelativeDepthSpacing
                & \\
            &
                & Damping
                & \GroundBlockAveragedSourcesRelativeDepthDamping
                & \BestGroundBlockAveragedSourcesRelativeDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{5}{*}{Variable}
                & Depth (m)
                & \GroundBlockAveragedSourcesVariableDepthDepth
                & \BestGroundBlockAveragedSourcesVariableDepthDepth
                & \multirow{5}{*}{
                    \BestGroundBlockAveragedSourcesVariableDepthRms
                  } \\
            &
                & Depth factor
                & \GroundBlockAveragedSourcesVariableDepthDepthFactor
                & \BestGroundBlockAveragedSourcesVariableDepthDepthFactor
                & \\
            &
                & K nearest
                & \GroundBlockAveragedSourcesVariableDepthKNearest
                & \BestGroundBlockAveragedSourcesVariableDepthKNearest
                & \\
            &
                & Spacing (m)
                & \GroundBlockAveragedSourcesVariableDepthSpacing
                & \BestGroundBlockAveragedSourcesVariableDepthSpacing
                & \\
            &
                & Damping
                & \GroundBlockAveragedSourcesVariableDepthDamping
                & \BestGroundBlockAveragedSourcesVariableDepthDamping
                & \\
        \midrule

        \multirow{4}{*}{Grid Sources}
            & \multirow{4}{*}{Constant}
                & Depth (m)
                & \GroundGridSourcesConstantDepthDepth
                & \BestGroundGridSourcesConstantDepthDepth
                & \multirow{4}{*}{
                    \BestGroundGridSourcesConstantDepthRms
                  } \\
            &
                & Spacing (m)
                & \GroundGridSourcesConstantDepthSpacing
                & \BestGroundGridSourcesConstantDepthSpacing
                & \\
            &
                & Damping
                & \GroundGridSourcesConstantDepthDamping
                & \BestGroundGridSourcesConstantDepthDamping
                & \\
    \end{tabular}
\end{table*}

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic airborne survey. The table also contains the set of
        parameters that generates the best prediction for each source
        distribution and its corresponding RMS score (in mGal).
    }
    \label{tab:parameters-airborne-survey}
    \begin{tabular}{c c l c c c}
        \textbf{Source layout}
            & \textbf{Depth type}
            & \multicolumn{1}{c}{\textbf{Parameters}}
            & \textbf{Values}
            & \textbf{Best}
            & \textbf{RMS} \\
        \toprule

        \multirow{8}{*}{Source Below Data}
            & \multirow{2}{*}{Constant}
                & Depth (m)
                & \AirborneSourceBelowDataConstantDepthDepth
                & \BestAirborneSourceBelowDataConstantDepthDepth
                & \multirow{2}{*}{
                    \BestAirborneSourceBelowDataConstantDepthRms
                  } \\
            &
                & Damping
                & \AirborneSourceBelowDataConstantDepthDamping
                & \BestAirborneSourceBelowDataConstantDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{2}{*}{Relative}
                & Depth (m)
                & \AirborneSourceBelowDataRelativeDepthDepth
                & \BestAirborneSourceBelowDataRelativeDepthDepth
                & \multirow{2}{*}{
                    \BestAirborneSourceBelowDataRelativeDepthRms
                  } \\
            &
                & Damping
                & \AirborneSourceBelowDataRelativeDepthDamping
                & \BestAirborneSourceBelowDataRelativeDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{4}{*}{Variable}
                & Depth (m)
                & \AirborneSourceBelowDataVariableDepthDepth
                & \BestAirborneSourceBelowDataVariableDepthDepth
                & \multirow{4}{*}{
                    \BestAirborneSourceBelowDataVariableDepthRms
                  } \\
            &
                & Depth factor
                & \AirborneSourceBelowDataVariableDepthDepthFactor
                & \BestAirborneSourceBelowDataVariableDepthDepthFactor
                & \\
            &
                & K nearest
                & \AirborneSourceBelowDataVariableDepthKNearest
                & \BestAirborneSourceBelowDataVariableDepthKNearest
                & \\
            &
                & Damping
                & \AirborneSourceBelowDataVariableDepthDamping
                & \BestAirborneSourceBelowDataVariableDepthDamping
                & \\
        \midrule

        \multirow{11}{*}{Block Averaged Sources}
            & \multirow{3}{*}{Constant}
                & Depth (m)
                & \AirborneBlockAveragedSourcesConstantDepthDepth
                & \BestAirborneBlockAveragedSourcesConstantDepthDepth
                & \multirow{3}{*}{
                    \BestAirborneBlockAveragedSourcesConstantDepthRms
                  } \\
            &
                & Spacing (m)
                & \AirborneBlockAveragedSourcesConstantDepthSpacing
                & \BestAirborneBlockAveragedSourcesConstantDepthSpacing
                & \\
            &
                & Damping
                & \AirborneBlockAveragedSourcesConstantDepthDamping
                & \BestAirborneBlockAveragedSourcesConstantDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{3}{*}{Relative}
                & Depth (m)
                & \AirborneBlockAveragedSourcesRelativeDepthDepth
                & \BestAirborneBlockAveragedSourcesRelativeDepthDepth
                & \multirow{3}{*}{
                    \BestAirborneBlockAveragedSourcesRelativeDepthRms
                  } \\
            &
                & Spacing (m)
                & \AirborneBlockAveragedSourcesRelativeDepthSpacing
                & \BestAirborneBlockAveragedSourcesRelativeDepthSpacing
                & \\
            &
                & Damping
                & \AirborneBlockAveragedSourcesRelativeDepthDamping
                & \BestAirborneBlockAveragedSourcesRelativeDepthDamping
                & \\
            \cmidrule{2-6}
            & \multirow{5}{*}{Variable}
                & Depth (m)
                & \AirborneBlockAveragedSourcesVariableDepthDepth
                & \BestAirborneBlockAveragedSourcesVariableDepthDepth
                & \multirow{5}{*}{
                    \BestAirborneBlockAveragedSourcesVariableDepthRms
                  } \\
            &
                & Depth factor
                & \AirborneBlockAveragedSourcesVariableDepthDepthFactor
                & \BestAirborneBlockAveragedSourcesVariableDepthDepthFactor
                & \\
            &
                & K nearest
                & \AirborneBlockAveragedSourcesVariableDepthKNearest
                & \BestAirborneBlockAveragedSourcesVariableDepthKNearest
                & \\
            &
                & Spacing (m)
                & \AirborneBlockAveragedSourcesVariableDepthSpacing
                & \BestAirborneBlockAveragedSourcesVariableDepthSpacing
                & \\
            &
                & Damping
                & \AirborneBlockAveragedSourcesVariableDepthDamping
                & \BestAirborneBlockAveragedSourcesVariableDepthDamping
                & \\
        \midrule

        \multirow{4}{*}{Grid Sources}
            & \multirow{4}{*}{Constant}
                & Depth (m)
                & \AirborneGridSourcesConstantDepthDepth
                & \BestAirborneGridSourcesConstantDepthDepth
                & \multirow{4}{*}{
                    \BestAirborneGridSourcesConstantDepthRms
                  } \\
            &
                & Spacing (m)
                & \AirborneGridSourcesConstantDepthSpacing
                & \BestAirborneGridSourcesConstantDepthSpacing
                & \\
            &
                & Damping
                & \AirborneGridSourcesConstantDepthDamping
                & \BestAirborneGridSourcesConstantDepthDamping
                & \\
    \end{tabular}
\end{table*}
